Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
background star text

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey
\citep[SDSS DR9,][]{Ahn12}.
For each target, we return
all stars within 12\arcsec\ with $\Delta r < 8$ relative to each object
of interest.
Of the 31 stars in our sample, four have such a companion.
Unlike the original \kep\ field, the field for \KT\ \Ci\ is
well out of the galactic plane, so the rate of giant, distant background
stars is significantly lower.
We include all potential contaminants in Table 5.

In Table 5, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness.

For EPIC 201465501 and 201779067, the observed transit depth is
larger than each of these values, so we reject the possibility that
these events could be the eclipses of the background binaries detected
here.

For EPIC 201546283, the observed transit depth is nearly identical to
the maximum false positive depth.
The photometry for this potential contaminant is consistent with that
of an M3V star; for this object to cause the observed eclipse it must
be a total eclipse of two M3V stars.
However, in that case, the observed event would be exactly V-shaped,
with second and third contact occurring simultaneously.
Since the transit is not V-shaped, it must be the result of
a relatively small body passing in front of a relatively large body.
Therefore, it cannot be caused by this observed background dwarf star.

For EPIC 201295312, the transit depth is significantly shallower than
the maximum false positive depth, so we cannot immediately
reject the hypothesis that the transit is actually a false positive
induced by a background eclipsing binary.
However, from the transit shape alone we can place a FPP of this
system of $1.1 \times 10^{-4}$.

SDSS is 95\% complete at $r=22.2$ and the telescope has a point
spread function of $1\farcs4$. In all cases except the four above, we
treat the SDSS data as providing a contrast curve at wide separations
down to a limiting magnitude of $r=22.2$.

>>>>

To investigate the possibility that such wide companions exist, we
query the ninth data release of the Sloan Digital Sky Survey
\citep[SDSS DR9,][]{Ahn12} for all stars within 25\arcsec\ with
$\Delta r < 8$ relative to each object of interest.  
Each such companion star has a ``maximum depth'' that it could cause
as a diluted ``transit'' signal, corresponding to a total eclipse 
of the hypothetical 
background binary system, inducing a 50\% flux decrement in the 
background star's apparent brightness.
Table 5 lists the 11 such stars (plus one detected in AO imaging),
whose maximum depth is at least as deep 
as the observed transit depth, thus making them possible contaminants.

The photometric apertures used to detect these candidates range in radius from
$10\farcs0$ to $19\farcs9$.  In order to be a plausible contaminant,
any companion star must
be either within this aperture or just outside but bright
enough for signficant flux to leak in.  
Evaluating each of the systems listed in Table 5, we judge that we cannot yet
rule out contamination as a potential source of the transit signal for four 
candidates: 201295312.01, 201403446.01, 201546283.01, 201828749.01.  Despite receiving
low FPP scores from \texttt{vespa}, we list these systems as candidates in
Table 4, rather than planets.  Further updates to the \texttt{vespa} code 
will allow consideration of ``specific'' false positive scenarios; that is, 
scenarios that correspond to actually detected stars such as these, rather than 
hypothetical background or bound companions.

The candidates with identified companions that we judge to not be plausible 
sources of potential contamination are the following:
\begin{itemize}

\item 201546283.01--- For this system, the ``maximum depth// is nearly 
identical to the observed transit depth, which would require a perfectly
V-shaped eclipse to explain.  As this is not the case (see Figure 2), 
this signal cannot
be caused by contamination from this star.

\item 201629650.01--- The companion to this star is $17\farcs3$ from
the EPIC target.  As this is outside the aperture 
(radius $15\farcs9$) and the background star is not particularly bright, 
we rule out contamination for this system.

\item 201702477.01--- The companion to this star is $12\farcs15$ from the
EPIC target, and the aperture size is $10\farcs0$.  In addition,
the maximum depth in this system is almost identical to the transit depth.
For these two reasons we rule out contamination in this case.

\end{itemize}

SDSS is 95\% complete at $r=22.2$ and the telescope has a point
spread function of $1\farcs4$. 
For the purposes of the \texttt{vespa} calculation, we thus
treat nondetection in SDSS data as providing a contrast curve at 
wide separations
down to a limiting magnitude of $r=22.2$.
